%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\faSuitcase \enskip Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Gojek} % Organization
    {DKI Jakarta} % Location
    {Aug. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained \& developed new features for GO-SHOP's order management system}
        \item {Bootstrapped GO-LAUNDRY's runnr allocation system in Golang}
        \item {Stacks: Golang, Ruby on Rails, PostgreSQL, Redis, Apache Kafka}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Shopee} % Organization
    {DKI Jakarta} % Location
    {Jul. 2018 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built robust \& reliable backend microservices for various high-traffic and demanding backend projects}
        \item {Highlight projects: Shopee's "Golden Ticket", Event Ticket Processing, Notification Service, Shopee's Ramadhan Infographic}
        \item {Stacks: Golang, Beego framework, MySQL, CloudSQL, Redis, RabbitMQ, Google Pubsub, Docker, Kubernetes}
      \end{cvitems}
    }
%---------------------------------------------------------



%---------------------------------------------------------
  \cventry
    {Research Intern \& Project Manager} % Job title
    {Institute for Pure \& Applied Mathematics} % Organization
    {Hong Kong} % Location
    {Jun. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project: "Efficient Communication in Distributed Machine Learning" sponsored by Microsoft Research Asia}
        \item {Investigated the effect of communication frequency in distributed Stochastic Gradient Descent (SGD)}
        \item {Performed the experiment on Logistic Regression, Convolutional Neural Network and Long-Short Term Memory RNN}
        \item {Stacks: CNTK, Python}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Altitude Labs} % Organization
    {Hong Kong} % Location
    {May 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote MySQL database integration code using Django Web Framework.}
        \item {Wrote basic REST APIs using Django REST Framework.}
        \item {Stacks: Django, Python, MySQL}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
